\documentclass{article}
\usepackage{color}
\usepackage{parskip}
\usepackage{longtable}
\usepackage{tabularx, tabularray}
\usepackage{caption}
\usepackage{blindtext}
\usepackage[margin=25mm]{geometry}
\pagenumbering{gobble}
\usepackage{lipsum}

\begin{document}

\color{red}
\section*{Term Glossary}

\color{black}
\centering
\begin{longtable}{|p{.19\columnwidth}|p{.250\columnwidth} |p{.20\columnwidth}|p{.30\columnwidth}|}


\hline

\textbf{Term} & \textbf{Description} & \textbf{Synonyms} & \textbf{Connection}
\\\hline
User &	People who can access the database system & Members, Leaders, Teams, Stakeholders, &	Financial Office, Branch office, Coordinator Office and Generalate Main Office, TAG. 
\\\hline 
Branch Office & The employees of  the branch office that will insert the request in the system & Branch Team & User, Proposal, Report, Project, Financial Office, Generalate, , TAG, Deadline and Budget.\\\hline 
Financial Office & The employees of the main office responsible for the budget & Financial Team & Project, Branch Office, TAG, Budget, Funds, and Generalate \\\hline 
Coordinators Office  & The employees of the main office responsible to define the type of the project & Coordinators Team & Branch Office, Generalate Main Office, Type, TAG, Report, Proposal. \\\hline 
Generalate Main Office & The decision makers for the project evaluation & Generalate Leadership Team, Generalate & Project, Proposal, Branch Office, Financial Office, Coordinators Office, Branch, TAG, Funds, Deadline, Budget, Report, and Deadline.  \\\hline 
Branch & The local offices of the organization, other than the main office, where the same activities are conducted. & Local office & Branch Office, Area\\\hline 
Proposal & The request from the branch for undertaking a particular project. & Offer, Application & Generalate Main Office, Branch Office, Coordinators office, Type and TAG \\\hline
TAG & The name assigned to a variable to be monitored. & Property, token, Unique ID. & Users and Reports \\\hline 
Funds & The amount of money available that has been raised through the benefactors. & & Generalate, Benefactors\\ \hline
Deadline & Date for requesting projects and status of Status change &  & Generalate team, Province team, Region team, Mission team, financial team \\\hline
Area & The site where the projects are being proposed or are in progress or have been completed. & & Project, Type, and Proposal.  \\\hline
Budget & The maximum or minimum amount of money needed for the project  & Project Site  & Proposal, Project, Generalate Main Office, Financial Office, Branch Office. \\\hline
Type & The classification of a project based on the field of interest & Field or classification & Coordinators Office, Project, Proposal, Branch Office and Budget. \\\hline
Report & The physical document that describes the details of the project  & & Generalate Main Office, Project \\\hline




\end{longtable}

\end{document}
